Template for indicator documentation

### 2023-09-12 DRAFT_insectIndicators.Rmd
cache data

```{r}
connect_to_insect_db()
```

@@

@@

```
```{r, echo = FALSE}
poll_loc_year %>% 
  slice(1:5) %>% 
kableExtra::kbl()
```

@@

```{r}
semi_loc <- get_localities(dataset = "NasIns",
                           habitat_type = "Semi-nat")

norway_regions <- get_map()
```

@@

diff_poll_richness_boot2 <- poll_richness_boot %>%
  boot_contrast(year == 2020 & region_name == 'Østlandet')
```
```{r}
diff_poll_richness_boot2
```

@@

We connect to the internal database with a convenience function.
```{r}
bombLepiSurv::humlesommerfConnect()
```

@@

```{r, fig.cap = "Bumblebees in grasslands 2021"}
allBombusGrassland2022 <- getAllData(type = "bumblebees",
                                     habitat = "gressmark",
                                     year = 2022,
                                     language = "norsk")

@@

@@

```{r}
bombus_trond_2022 <- getComplData(type = "Humler",
                                  region_short = "Trond",
                                  habitat = "Gressmark",
                                  year = 2022)
```

@@

```{r}
exp_bombus_trond <- getExpValues(type = "Humler",
                                 region_short = "Trond",
                                 habitat = "Gressmark")
```

@@

```
```{r}
getAmountWeights()
```
Lastly, we specify the number of samples for the bootstrap. To speed up, only 999 samples is shown here.

>>>>

```{r, eval=FALSE}
connect_to_insect_db()
```

@@

```{r, eval=FALSE}

@@

```{r, echo = FALSE}
poll_loc_year <- readRDS("data/cache/poll_loc_year.RDS")
poll_loc_year %>% 
  slice(1:5) %>% 
kableExtra::kbl()
```

@@

```{r, eval=FALSE}
semi_loc <- get_localities(dataset = "NasIns",
                           habitat_type = "Semi-nat")

```{r, echo=FALSE}
semi_loc<-readRDS("data/cache/semi_loc.RDS")
```

```{r}
norway_regions <- get_map()
```

@@

diff_poll_richness_boot2 <- poll_richness_boot %>%
  boot_contrast(year == 2020 & region_name == 'Østlandet')
```

```{r}
diff_poll_richness_boot2
```

@@

We connect to the internal database with a convenience function.
```{r, eval=FALSE}
bombLepiSurv::humlesommerfConnect()
```

@@

```{r,eval=FALSE, fig.cap = "Bumblebees in grasslands 2021"}
allBombusGrassland2022 <- getAllData(type = "bumblebees",
                                     habitat = "gressmark",
                                     year = 2022,
                                     language = "norsk")

@@

```{r, echo=FALSE}
allBombusGrassland2022<-readRDS("data/cache/allBombusGrassland2022.RDS")
```

@@

```{r, eval=FALSE}
bombus_trond_2022 <- getComplData(type = "Humler",
                                  region_short = "Trond",
                                  habitat = "Gressmark",
                                  year = 2022)
```

```{r, echo=FALSE}
bombus_trond_2022<-readRDS("data/cache/bombus_trond_2022.RDS")
```

@@

```{r, eval=FALSE}
exp_bombus_trond <- getExpValues(type = "Humler",
                                 region_short = "Trond",
                                 habitat = "Gressmark")
```

```{r}
exp_bombus_trond<-readRDS("data/cache/exp_bombus_trond.RDS")
```

@@

```{r}
getAmountWeights()
```
Lastly, we specify the number of samples for the bootstrap. To speed up, only 999 samples is shown here.
